\chapter{She Comes First}{Ian Kerner}
\emph{Disclaimer:} because this is a book about female sexual pleasure, it also comes with unnecessarily feminist berating and victim-playing. There is a noticeable undertone of "men are ignorant", "men have always oppressed women by only caring about their own pleasure", and so on, which must all be untrue given that evolution refined women's anatomy so much for non-reproductive pleasure. If men never gave them that pleasure, they wouldn't have the machinery. The obsession with power play is also cringe,  claiming that "it's worshipping/vulnerable/subby to go down on a woman" which is clearly wrong if you've ever seen a woman in a state of enjoyment.

Also, the author is a sexologist and likes to cite Alfred Kinsey, who was an absolute weirdo freak who sexually harassed all his colleagues and let pedophiles rape children on camera and used that to generate bogus statistics. He also cites Masters \& Johnson, the research couple that was apparently so good at giving relationship advice that they eventually divorced.

\section*{Introduction}
\begin{outline}
\1 This is a book about pussy licking, a.k.a.\ "cunnilingus" (CL).
Oral sex is real sex, not foreplay. There is no wrong way to have an orgasm. CL has a beginning, middle and end, like a session of intercourse would.
\1 Common complaints from women: guys don't like CL, or lack the skill, or don't do it enough (hey, kinda like blowjobs!).
\1 The "outercourse" model: the man's gratification, which is via internal penetration, should be delayed until after the woman's first orgasm, which is via external stimulation.
\1 Book parts:
\begin{enumerate}
	\item Why lick pussy
	\item How to lick pussy
	\item When to lick pussy
\end{enumerate}

\1 Some interesting facts:
	\2 The clitoris has 18 parts.
	\2 The majority of the nerve endings contributing to female orgasm are not inside the vagina but spread across the outside of the genitalia. Intercourse was never meant to make women orgasm because the clitoris lies too high.
	\2 Women often need 15 minutes to become aroused enough to be able to orgasm.
\1 In a study where 98 married women kept a sex diary, it was reported that:
	\2 The category of "very satisfying" was given to CL by 82\%, and to intercourse by 68\%, a 14\% gap.
	\2 Orgasm happened 25\% of the intercourse sessions but 81\% for the CL sessions, a 56\% gap.
\1 Don't rub a clitoris like you rub an eraser.
\1 Every woman is different, but being good at general technique always pays off. It helps to have a stable partner so you can iterate, and so that your sex actually has purpose (bonding).
\end{outline}

\bookpart{}
\section{The Courtesy That Counts}
\begin{outline}
\1 Male sexuality is quite unique in that it suffices to stimulate one body part. Women need touch in many places and need a mental connection.
\1 The first orgasm of a session is the most difficult. Three ingredients: relaxation (by her), concentration, stimulation (by me).
\1 In general, $<$30\% of women orgasm each session. With at least 21 minutes of foreplay, it jumps to $>$90\%.
\1 A man's orgasm is better when he is aroused for a while. What better way to kill time than to pleasure your woman?
\end{outline}

\section{Her Clitoris}
\begin{outline}
\1 The clitoris is quite a large organ; you only see the head, but it has legs that extend downwards on either side, like a boomerang shape.
\1 The clitoris has 8000 nerve fibers dedicated to it. That's a lot, since the pelvis only has 15000 in total (not sure if the 8000 is in that).
\1 The clitoris is hence not that small pea, but more like a network of roots.
\1 The clitoral head is homologous to the head of the penis. Shouldn't be difficult to imagine the sensation as a man.
\end{outline}

\section{Think Outside Her Box}
\begin{outline}
\1 The inner 2/3 of the vagina are much less sensitive than the outer 1/3.
\1 CL allows guys to stop worrying about size, stamina or penetrative technique.
\end{outline}

\section{Female Orgasm: Keep It Simple}
\begin{outline}
\1 In pop culture, the distinction exists between vaginal, G-spot and clitoral orgasms, but actually, the clitoris is the stimulation centre for all of these.
\1 Women born without vaginas (that is: actual women with a birth defect, not the Orwellian term for confused men) can still orgasm, but those without a clitoris (e.g. due to female circumcision) can't.
\1 The G-spot is probably the back of the clitoris being hit through the vaginal wall.
\1 When you penetrate as deep as you can, she might not be stimulated by how deep you reach on the inside, but actually by your pubic bone touching her vulva.
\1 During arousal, a blood-filled horseshoe swells around the vaginal opening to increase friction at the base.
\end{outline}

\section{The Tongue is Mightier Than the Sword}
\begin{outline}
\1 Benefits of the tongue that the penis doesn't have:
	\2 Functionality not dependent on our level of arousal;
	\2 Can go for a second round;
	\2 Very precise control;
	\2 Useful in hard and in soft mode;
	\2 Doesn't get friction burns;
	\2 Works even if you have penile problems (e.g. premature ejaculation, impotence, ...).
\1 Complaints by women about technique: lack of consistent rhythmic pressure; too rough and impatient; don't finish the job after it was started.
\1 The author backs up his point with a bizarre deference to "experienced women who use vibrators" finding CL to stimulate them better than sex, as if vibrators don't destroy your healthy stimulation baseline.
\end{outline}

\section{Her Inner Goddess}
\begin{outline}
\1 Philosophers used to think equally of the male and female orgasm.
\end{outline}

\section{Avoid Freud}
\begin{outline}
\1 Freud bad because he said real women learn to love vaginal over clitoral stimuli.
\1 Anyway, one woman's testimony says that CL is a turn-on because she receives his full attention and focus.
\end{outline}

\section{What's in a Name?}
\begin{outline}
\1 Yay, a diagram!
\1 The external genitals of a woman (lips and even Venus mound) are collectively referred to as "vulva".
\end{outline}

\section{Visible Female Sexual Anatomy}
The vulva consists of:
\begin{outline}
\1 \emph{Venus mound}: the skin between the belt line and the rest. Becomes fatter with puberty and grows pubic hair, whose purpose is to trap pheromones.
\1 \emph{Labia majora}: the two skin folds that separate the skin of her legs with the skin of the vulva. Has pubic hair towards the legs and sweat/oil glands towards the vulva. Homologous to our ballsack (just the sack) but not too sensitive.
\1 \emph{Front commissure}: the labia majora don't meet at the top, but are separated by 1 cm. That's the front commisure, and it hides the shaft of the clitoris. Women rub this when they masturbate.
\1 \emph{Labia minora}: the violin-shaped fleshy wings surrounded by the labia majora. Very sensitive. Have oil glands. Meet in one place at the bottom (the \emph{fourchette}) and in two places at the top (above and below the clitoral head, one making the hood and the other making the frenulum).
\1 \emph{Vestibule}: visible surface surrounded by labia minora. Hosts the urethral opening at the top and the introitus (vaginal opening) in the middle.
\1 \emph{Hood (prepuce)}: sits over the clitoral head. Homologous to foreskin. Rubbing it is enough sensation.
\1 \emph{Frenulum (bridle)}: skin just below the clitoral head. Very sensitive.
\1 \emph{Clitoral head}: like the penile head, except with double the nerve endings. Connected to a ligament (in turn connected to the ovaries) that pulls it under the hood during climax because she would otherwise die of stimulation.
\1 \emph{Taint (perineum)}: between fourchette and anus. Has erectile sponge underneath.
\end{outline}

Anatomy lessons (where else are you going to find HD close-ups of an aroused woman bruh):
\begin{outline}
\1 \url{https://www.pornhub.com/view_video.php?viewkey=65022886780e9}
\1 \url{https://www.pornhub.com/view_video.php?viewkey=ph621ca62f2bd61}
\end{outline}

\section{Invisible Female Sexual Anatomy}
\begin{outline}
\1 \emph{Clitoral shaft}: under the commissure. Very sensitive and becomes erect.
\1 \emph{Clitoral legs (crura)}: horseshoe under the labia minora that connect to the shaft.
\1 \emph{Bulbs}: erectile sponge around the introitus that makes the vagina tighter at the start to give a penis more friction there.
\1 \emph{Kegel muscle}: the one that stops you from peeing and contracts during orgasm.
\1 \emph{Oval muscle}: for contracting the vagina. Sits on top of the bulbs.
\end{outline}

\section{Avoid G-spotty Logic}
\begin{outline}
\1 Between the urethra and the vagina is urethral sponge that is there to cushions the urethra against damage during sex.
\1 This is "the \emph{G-spot}". Some call it the "\emph{clitoral cluster}".
\1 It's sensitive, but not that much. Responds best to "persistent massaging pressure" but she might pee because of it. It feels good because it's the closest you get to the clitoral head from the bottom.
\end{outline}

\section{Female ejaculation}
\begin{outline}
\1 There's a tiny bit of moisture that comes from around the urethra (para-urethral glands) and is supposedly homologous to prostate fluid. If it gushes, it's coming from the bladder and it's piss.
\1 Female "ejaculation" doesn't enhance orgasm.
\end{outline}

\section{How Wet Is Wet?}
\begin{outline}
\1 The vagina lubricates itself by "sweating" across the entire wall.
\1 There are also two glands, Bartholin's glands, that excrete a bit of very thick lubricant. It's unclear to me if these are parallel to the vagina (lubricating the vestibule) or perpendicular (lubricating the introitus).
\1 During arousal, the vagina elongates and widens in the deeper 2/3.
\1 And here we discover that the claim about "18 parts of the clitoris" is bullshit made up by feminist pagans, including pelvic floor muscles, the sponge beneath the taint, the labia minora... Those are not the clitoris.
\end{outline}

\section{Aristotle and the Poetics of Arousal}
\begin{outline}
\1 Sex should follow a narrative arc, which according to Aristotle means that 
\begin{enumerate}
	\item the stages should be in correct order;
	\item one stage can only happen after successful completion of the previous stage.
\end{enumerate}
\1 \emph{EPOR}: 
\begin{enumerate}
	\item excitement
	\item plateau
	\item orgasm
	\item resolution/relaxation.
\end{enumerate}
\end{outline}

\section{A Synopsis of Female Sexual Response}
\begin{outline}
\1 During foreplay:
	\2 Blood rushes to the pelvic region, causing tissues to swell and fluid to push through the vaginal walls.
	\2 Skin across the body becomes sensitive.
	\2 Breasts swell and nipples become primed to release oxytocin when stimulated.
	\2 The clitoral head might emerge.

\1 During CL:
	\2 Heartbeat and breathing frequency increase. Breathing deepens. Muscles tense.
	\2 Introitus tightens, vagina elongates.
	\2 Clitoral body (shaft, legs, bulbs...) stiffens and extends downward. Clitoral cluster expands and can be felt on the vaginal ceiling.
	\2 Suspensory ligament retracts clitoral head.
	\2 Round ligament pulls on uterus.

\1 Nearing orgasm:
	\2 Skin flushes.
	\2 Deep breaths.
	\2 Inner labia become dark.

\1 On orgasm:
	\2 Vagina contracts.
	\2 Uterus contracts due to oxytocin.
	\2 Pelvic floor muscles (around the vagina and anus) contract ~6-10 times at 1/0.8 Hz.

\1 After orgasm, males and females both can't tolerate more stimulation, but they differ in the timeframe:
	\2 Male: lose erection quickly (1-2 minutes), recover slowly (a day).
	\2 Female: lose erection slowly (5-10 minutes), recover quickly (almost instantly).
	\2 Women want to cuddle after orgasm due to the oxytocin, men want to go to sleep. If you can't hold off the sleep, do it while cuddling.

\1 Fun facts:
	\2 Orgasms in pregnant women are longer because their genitals are enlarged.
	\2 The clitoral head doubles in size when aroused.
	\2 Men only have 4-6 contractions on orgasm.
\end{outline}

\section{Scent and Sensibility}
\begin{outline}
\1 50\% of men who performed CL have their reservations due to bad smell/taste.
\1 The vagina is acidic by nature since it cleans itself with presence of lactobacilli, which are oxygen-friendly anaerobic bacteria.
\1 Bad smells are caused by:
	\2 Dried sweat and/or discharge. Solution: shower better.
	\2 Lack of lactobacilli and instead more purely anaerobic bacteria. Solution: antibiotics, because that's BV (bacterial vaginosis). Also eat more yoghurt.
	\2 Other issues like substance use (medication, alcohol, drugs, tobacco), dehydration, vitamin deficiencies, or other infections or STDs.
	
\1 Sperm throws off the pH too because it is alkaline, not acidic.
\end{outline}

\section{We've Come a Long Way}
One of the most self-owning chapters ever written. A summary of what is bad about it:
\begin{outline}
\1 Cites the 1953 Kinsey report. You do not want to cite the 1953 Kinsey report.
\1 Calls it "boring" to have a societal standard that prefers oral sex to be reserved to committed relationships.
\1 Frames it as problematic that "only 3\% of younger women who were still virgins reported ever receiving CL". Yeah, because they're virgins, stupid. Also, this book opens with "oral sex is real sex", so then those 3\% don't even count as virgins anymore according to your own definition.
\1 Frames it as a success story that "twice as many women who went to college have given or received oral sex as compared to those who did not finish high school, and twice as many of those better-educated women had or received oral sex the last time they had sex". Please explain to me how loser jocks pumping and dumping girls on campus is a good thing.
\1 In 1994, 84\% of women who viewed sex as recreational had oral sex in the last year, 74\% of women who maintained it should be part of a loving relationship, and 56\% of women who didn't believe in premarital sex. But... the study didn't control for marital status... so this says nothing about the sexual satisfaction of married traditional women.
\1 Claims that the increase in CL prevalence is due to "young women becoming more confident and assertive in their demand for a level playing field". This is a stupid statement for many reasons:
	\2 Demanding sexual acts doesn't make you confident nor assertive. It's weird. Many many married men never get blowjobs. Should we praise them for demanding a level playing field?
	\2 Is it really a compliment to your society that women are increasingly becoming annoying, activist crusaders? Who is attracted to this? Whatever happened to having a loving relationship with healthy communication and reciprocity?
	\2 If you want to turn off men from giving CL, you should definitely market it as the woman receiving it having dominating power over the man giving. The same goes for calling CL an act of submission by the man. You are putting your idiotic ideological obsession over your sexual pleasure. You really can't get out of your own way, can you?
\end{outline}

\section{But Proceed With Caution}
\begin{outline}
\1 As usual, there are 4 incurable STDs: HIV/AIDS, HBV/hepatitis, HPV/warts, HSV/herpes.
\1 STDs can be transmitted from vulva to mouth and vice versa.
	\2 Vaginal secretions and menstrual blood contain HIV if the woman has it.
	\2 Men can transmit it via mouth wounds (e.g. from brushing your teeth or flossing).
\1 1/6 people are infected with an STD in their life, and those who get one more than once are likely to have had one in the last year, at the same rate of unwanted pregnancies.
\1 The sexual revolution can't stop taking Ls:
	\2 More women have had an STD than men.
	\2 Women are twice as likely to have genital warts and more than twice as likely to have herpes.
	\2 The best predictor of catching an STD is being promiscuous. 1/3 of those with a body count over 20 have caught an STD.
\1 Promiscuity correlates with multiple other risk-inducing factors:
	\2 Body count correlates with the body count of partners. That is: if you sleep with many people, the people you sleep with also sleep with many people, which means you are at exponential risk for STD transmission, not linear.
	\2 Body count correlates negatively with how acquainted one is with their sexual partners.
	\2 Body count correlates to having sex with impeded cognition (i.e. alcohol/drugs).
\end{outline}

\section{Eat Right}
\begin{mdframed}
\textbf{DO NOT} TAKE THE RISK IF YOU ARE UNCERTAIN ABOUT DISEASES. NO REWARD IS WORTH A LIFETIME OF REGRET AND DISCOMFORT.
\end{mdframed}

\begin{outline}
\1 If you insist, use a barrier like a dental dam ("bef-lapje"). Problem: guys don't have them in house and girls are offended by the implication of having a disease.
\1 Even this feminist book cannot deny that a "loving, trusting relationship" leads to the least risky, least offensive and most pleasurable sex. If you think about it, this is THE STRONGEST endorsement you could possibly get for conservative sexuality: despite praising how great it is that college women are being rammed by chads who dispose of them like a used condom, they cannot deny the better alternative.
\end{outline}

\section{The CL Manifesto}
\begin{outline}
\1 It's much harder to perform CL on a woman when she detects in you:
	\2 ambivalence (you're not sure if you want to do it)
	\2 insincerity (you don't like doing it)
	\2 impatience (you are pressuring her to orgasm)
	
\1 You have to be committed.

\1 You have to tell her these three assurances:
\begin{enumerate}
	\item You enjoy giving her CL.
	\item She can take her time, we're not in a rush.
	\item Her scent is a plus, because it reminds you of sex. (The book has a much too simp-y variation.)
\end{enumerate}

\1 If she has fears, talk through those fears with her. Be her guidance. That in itself is sexy.
\end{outline}


\section*{PART 2}
\section{A Note on the Play Process}
\begin{outline}
\1 CL is not foreplay, because it is the best way to make a woman orgasm, and orgasming is the core of sex, not foreplay.
\1 The "play process" is a 3-phase framework for all sex sessions.
\begin{enumerate}
	\item \emph{Foreplay}: teasing to get each other aroused. Perhaps you get some light head, but definitely not until orgasm.
	\item \emph{Coreplay}: CL until her 1st orgasm.
	\item \emph{Moreplay}: you are free to give her a 2nd, 3rd, ... orgasm, and/or she gives you head and/or intercourse until you orgasm.
\end{enumerate}
\end{outline}

\section{Foreplay}
Here is a list of things to give you inspiration for foreplay.
\begin{outline}
\1 Anticipation: give subtle hints to make her expect a play session soon. Carress her neck as you walk by. Use your eyes to signal desire. Whisper dirty words.

\1 Avoidance: \textbf{DO NOT} touch her genitals for the first 15 minutes of the session. Women need full-body and psychological stimulation to become genitally aroused.

\1 Awareness: don't lose focus once you start your session. Be present with her. Don't be distracted. Every act should be geared towards playing.

\1 Bathing/showering together: two birds with one stone. She is clean and horny after!

\1 Skin: female skin is thinner, less hairy and denser with nerve endings (because women are smaller whilst having the same amount of neurons), so she really feels touch everywhere.

\1 Breasts: touching her breasts turns the man on more than the woman. Be very gentle with them. (Although I must admit that the one set of titties I have suckled in my life did not belong to my mother.)

\1 Breathing: wetness can be an indicator of arousal, but much better is her breathing rhythm and the tightness of her abs.

\1 Breath: \textbf{DO NOT} brush your teeth or floss before CL. This creates micro-wounds that can make you transmit or receive STDs. Use a not-too-abrasive mouthwash.

\1 Lighting: men prefer lights on, women prefer lights off. Solution: candlelight or (for moderns who don't enjoy fire hazards) diffuse, dimmed, warm LED light.

\1 Criticism: \textbf{DO NOT} criticise your partner sexually. Criticism is the death of sex. If you want something from them, point to what they are doing that is in line with it, compliment it, and ask for more. See \url{https://youtube.com/shorts/cb4MgNklqOo}

\1 Communication: keep the feedback channel open. Before, during and after. The best predictor of sexual marital satisfaction in a survey of 100 000 women was talking about sex with their husband.

\1 Fantasy:
	\2 Men and women tend to fantasise differently. The book says men have visual fantasies and women have story-based fantasies, but I think that's wrong. Men fantasise about being seduced (by a teacher, a girl at a café, ...), women fantasise about taming a rough yet competent man (business man, surgeon, ...).
	\2 Reading erotica together is a great way to get in the mood. My opinion: don't take it too seriously. You could also have a laugh about the vulgarity and still roll into sex.
	\2 Some fantasies are only hot because they will never happen. BE CAREFUL bringing them into existence: you might not look at your partner the same way, and they might not enjoy their fantasy anymore. Do not take fantasies out of the bedroom.

\1 Blowjobs: as noted, a very light blowjob fits in foreplay, a proper blowjob fits in moreplay.

\1 Fingers: keep it through clothes during foreplay. You'll have plenty of opportunity for penetration during coreplay. Clip your nails.

\1 Hair: the book is hypocritical about it. Regarding her pubic hair, it's "her body, her choice". Regarding your facial hair, it's "her husband, her choice". My opinion: both people should cater to their partner's desire. (And no, it's not creepy to prefer bare over hairy. All the "real women have hair" femcels are suddenly real quiet when you ask them if they like a clean-shaven face)

\1 Dirty talk: over 90\% of men like when a woman does it (which matches my hypothesis about seduction above).

\1 Kissing: a woman's upper lip is apparently directly connected to her clitoris...? Kissing the upper lip is hot and dominant anyway.

\1 Lingerie: appreciate and don't tear.

\1 Lubricant: 20\% of women have trouble getting wet. For CL, saliva suffices. For fingering before CL, use a water-based lubricant. No oil-based and \textbf{DO NOT} use spermicide when your mouth will be near it.

\1 Music: keep it low-key to get into a trance.
Hand ties: if she has trouble surrendering, discuss tying her hands.

\1 Orgasm: if she already orgasms during foreplay (e.g.\ due to you fingering her, or her touching herself), \textbf{DO NOT} stimulate the vulva (especially the clitoral head) further for 5 to 10 minutes. Keep her warm and sexual by kissing and hugging instead.

\1 Penetration: there are two ways to use an erection for foreplay.
	\2 Grind between her labia, making contact with her clitoris;
	\2 Put in "just the tip" (either in and out or just stationary) while gently massaging the clitoral head.
\end{outline}

\section{Introducing Coreplay}
The coreplay phase itself has 6 substages:
\begin{enumerate}
	\item First kiss
	\item Establishment
	\item Tension
	\item Escalation
	\item Preorgasm
	\item Orgasm
\end{enumerate}

\section{Form Follows Function: Getting into Position}
\begin{outline}
\1 After taste, the most common reason guys don't like CL is physical pain.

\1 Position should optimise two things: sustainable giving and relaxed receiving.

\1 Wrong positions and why:
	\2 69: wrong tongue angle, can't use your hands, you can't stay on task because of the pleasure, she can't focus on receiving. If you use 69 as foreplay, \textbf{DO NOT} make contact with the vulva. Kiss her legs or something.
	\2 Face-sitting: can't use your hands, and she'll get back pain from being upright.
	\2 Against the wall: she can't relax her legs and your knees hurt.

\1 The right position:
	\2 Her: flat on her back, legs more together than apart(!), pillow under her butt and two pillows under her shoulders. When she gets more aroused, her back will curve towards your mouth, not away.
	\2 You: pillows under your forearms, in a straight line with her body. Nose touches her mons pubis, upper lip touches her front commisure, tongue should be able to envelop her vestibule.
\end{outline}

\section{Hotspots in the Clitoral Network}
The 10 important parts respond well to:
\begin{enumerate}
	\item Head and hood: gentle, rhythmic tongue strokes and firmer pressure once aroused.
	\item Clitoral cluster: firm finger pressure.
	\item Mons pubis: massage with base of hand.
	\item Front commissure: tongue strokes, and pressure from upper lip once aroused.
	\item Frenulum: tongue strokes and firm pressure.
	\item Labia minora: tongue strokes, nibbles and pinched.
	\item Introitus: slow, long licks and finger tickles.
	\item Fourchette: tongue strokes and finger tickles.
	\item Perineum: basically anything, but I ain't doing that.
	\item Anus: stay clear, there are bacteria here that cannot go into the vagina!
\end{enumerate}

\section{Grand Openings: The First Kiss}
\begin{mdframed}
\textbf{DO NOT EVER} BLOW INTO A VAGINA, NOT TO BE GOOFY AND NOT TO PLEASURE HER. SHE WILL ACTUALLY DIE FROM THIS.
\end{mdframed}

\begin{outline}
\1 The anticipation should be killing her. Before you make first contact:
	\2 Give her the 3 assurances and tell her how beautiful she is.
	\2 Really appreciate the sight.
	\2 Brush her mons pubis with your fingers.
	\2 Give soft kisses (just lips) on the inside of her legs, her underwear, and perhaps labia majora.

\1 The first kiss is one long lick:
\begin{enumerate}
	\item Start at the fourchette and move up.
	\item Move over the labia minora.
	\item Pause at the frenulum, which teases the clitoral head.
	\item Brush the head lightly.
	\item Push down on the front commissure with the tip of your tongue.
	\item Press one finger on her perineum and pull her mons pubis up with your other hand. This tightens the introitus and pulls the labia minora together.
	\item Long lick top to bottom.
	\item Rest your tongue flat and still against her entire vestibule. She will automatically gyrate her hips to pick up your saliva and create the first friction of this CL.
\end{enumerate}
\end{outline}

\section{Establishing Rhythm}
Consists of two supersets:
\begin{outline}
\1 Superset 1: 20 sets (3 minutes) of
	\2 5 seconds: one long, slow, bottom-to-top lick.
	\2 5 seconds: tongue flat and still, enveloping her vulva, allowing her to grind.
	\2 Break contact momentarily to get a small stimulation reset.

\1 Superset 2: 6 sets of
	\2 5, then 6, then 7, then 8 ... half licks from bottom to mid-vagina that explicitly avoid the clitoral head. This will make it come out from under the hood. This is the goal you keep in mind.
	\2 1 full lick that stops on the clitoral head.
	\2 5 seconds: soak the clitoral head to lubricate it and acclimate it to stimulation.

\1 Extra advice:
	\2 Keep this stage slow. It's a marathon, not a sprint. Don't meet passion with passion; keep control.
	\2 For the first superset, make sure you don't go so fast that one lick is still being enjoyed when the next one arrives.
	\2 Grab her legs and let her push against your hands. You can gauge how aroused she is by the muscular tension, and pushing against your hands causes buildup that will be released on orgasm.
\end{outline}

\section{Developing Tension, pt.1}
\begin{outline}
\1 Keep licking. Now your hands get involved.
\begin{enumerate}
	\item Place non-dominant hand under her butt (see p. 141 for an image) so that you can pull her in with your fingers/palm.
	\item While licking, tease the vulva by tracing one finger across the labia minora, the front commissure, the frenulum, the fourchette, and the base of the vagina.
	\item While licking, insert the first two knuckles of your index finger into her vagina. Make sure you:
	\begin{itemize}
		\item Hold straight and still. The goal is that she'll start contracting, not that you stimulate.
		\item Don't insert more than one finger. She can't reach it too much.
	\end{itemize}
	\item Use your thumb to rub the front commissure.
\end{enumerate}
\end{outline}

\section{Time Flies}
\begin{outline}
\1 How long should CL take? Until she orgasms.
\1 On average, not counting foreplay, that's 15-45 minutes. Just reserve an hour.
\end{outline}

\section{Developing Tension, pt. 2}
The following are some variations on normal tongue strokes:
\begin{outline}
\1 Cat licks: short licks on every part of the vulva before you soak the clitoral head.
\1 Horizontals: mix into verticals, going back and forth.
\1 Diagonals: tilt head and do a slow, dragging like with side of tongue.
\1 Better finger game: use thumbs to part labia, use index to rub front commissure.
\1 Shadowing: do the tongue strokes with your index finger instead of your tongue.
\1 Rope-a-dope: let her grind on your flat tongue until she needs a break, and then give a burst of licks to overwhelm her.
\1 Suction: gently suck the clitoral head, increasing bloodflow there.
\1 Alphabet: pick one letter and trace it (recommended is F).
\end{outline}

\section{Escalating the Action, pt. 1}
\begin{outline}
\1 Left hand: pressed down on pubic bone.
\1 Right hand: index finger inserted into the vagina so that when you straighten-bend-straighten-bend it ("come hither"), you're indenting the G-spot sponge. The base of your finger should press upwards.
\1 Tongue: flat against clitoral head.
\1 Finger should first do ceiling, then floor, then sides (staying close to the entrance).
\1 Optional: give her a perineal pinch, i.e. pinch the fourchette.
\end{outline}

\section{Two's Company}
Now that you have a finger inside:
\begin{enumerate}
	\item Insert middle finger too. Keep still to let her contract.
	\item Do a bit of "come hither" with two fingers, covering the four walls.
	\item Keep tongue flat on clitoral head and apply slight pressure. (Pressure is more important than movement now!)
	\item Flatten both fingers and press upwards on the vaginal ceiling while pressing down on the pubic bone. Massage like this for a while.
	\item Put non-dominant hand under her butt and raise dominant fingers to hook into her vaginal ceiling. Pull her in with force and start licking.
\end{enumerate}

\section{An Interlude}
\begin{outline}
\1 If she gets lonely while you're down there, keep your fingers hooked but give her boobs some attention.
\1 Stay clear of her mouth since she probably doesn't want to taste herself.
\end{outline}

\section{Escalating the Action, pt. 2}
Most important at this point is pressure. We're going to squeeze the orgasm out of her, and give as many points of resistance for her to rub against -- every direction she moves, she will be stimulated.
\begin{outline}
\1 Hands:
	\2 Right hand: two fingers hooked into the G-spot, thumb massaging frenulum.
	\2 Left hand: thumb massaging perineum.
\1 Mouth: alternating between three modes.
	\2 Short tongue licks.
	\2 10-second repetitions: press top lip/gum into the front commissure.
	\2 Flat, hard tongue still against her clitoral head.
\end{outline}

\section{A Stitch in Time}
\begin{outline}
\1 One of the most common complaints from women: guys are impatient and need to be SLOWER and GENTLER.
\1 Reminder that when she feels rushed, she won't come. Foreplay puts her at ease.
\end{outline}

\section{Preorgasm, pt. 1}
\begin{outline}
\1 Signs that she is generally close to orgasm, according to Master Wu:
	\2 Deep panting
	\2 Voice shakes uncontrollably and language is nonsensical
	\2 Eyes closed
	\2 Ears and face red
	\2 Vagina starts pulsing
\1 Other things guys have noticed:
	\2 Skin heats up
	\2 Breasts swell
	\2 Lubricant becomes thick and warm
	\2 Grabs you in a headlock
\1 Signs that orgasm is \emph{90 seconds away}:
	\2 Labia minora turn dark red
	\2 Clitoral head retracts under the hood (can be felt even in the dark)
\end{outline}

\section{Preorgasm, pt. 2}
\begin{outline}
\1 The challenge now becomes holding her in place. You need to be able to keep the same stimulation for 90 seconds.
	\2 Straddle her with your legs to hold her down.
	\2 Use a belt to tie her ankles.

\1 She needs to keep her legs together, in a straight line. The closer the legs (with your head and fingers coming in from the top) the easier the orgasm.
\end{outline}

\section{Posterior Pizzazz}
I'm not doing anal stimulation, IT IS DEVIANT AND THEREFORE WE DO NOT WANT IT.

\section{Preorgasm, pt. 3}
\textbf{DO NOT} meet passion with passion. Don't speed up because she speeds up.
\begin{outline}
\1 Tease the orgasm out of her, slowly:
	\2 Slow down licking pace and don't chase the orgasm, but let it come to you.
	\2 Skip every 3rd lick.
	\2 Randomly insert horizontal licks.

\1 Instead of regular licks, try these:
	\2 Start the lick on the flat side of the tongue, but whip it up to end in the tip.
	\2 Jab with the tip, like a frog catches flies.
	\2 Lightly jab, barely touching her.
\end{outline}

\section{A Note for Those Stuck Without an Ending}
\begin{outline}
\1 If she absolutely needs intercourse to orgasm (due to conditioning, not due to anatomy), keep your CL rhythm. Make the transition seamless.
\end{outline}

\section{The Female Orgasm}
\begin{outline}
\1 Many signs of a real orgasm are hard to fake:
	\2 15 vaginal contractions for 20 seconds.
	\2 Soaring heartrate to 180 BPM.
	\2 Nipples hardening afterwards.
	\2 Quickly losing the flushed face afterwards.
	\2 Being spasmodically hypersensitive about the clit being touched.

\1 Don't stop until she says so.
	\2 Women have no "point of no return": an orgasm can be stopped short.
	\2 Use ~5 tongue jabs to fuel the orgasm throughout its 20 seconds.
\end{outline}

\section{Moreplay: She Comes Again (and Again)}
\begin{outline}
\1 All women are multiorgasmic.
\1 After orgasm, the vulva needs 10 minutes to get back to normal, but her hormones are not. Result: subsequent orgasms, e.g. due to penetration, become much easier.
\end{outline}

\section{Seamless Transitions}
\begin{outline}
\1 If you want to go to intercourse, do a little more CL to get her close to her 2nd orgasm.
\1 To allow orgasm during penetration, you need clitoral stimulation:
	\2 Cowgirl allows her to grind her clitoral head on your pubic bone, and set the pace.
	\2 Missionary when you penetrate from a higher angle (CAT) allows you to grind into her.
\end{outline}

\section{Achieving Simultaneity}
\begin{outline}
\1 To orgasm simultaneously, keep movement simple.
\1 Much easier in committed relationships because the trick is to know each other's bodies.
\end{outline}

\section{Don't Forget Your Epilogue}
Cuddle, kiss, and whisper romantic words for 15 minutes after.

\section{The Substance of Style}
A list of key ideas, e.g. the flat tongue to grind on, the closed legs, ...

\section{Routines: A Cheat Sheet}
\begin{outline}
\1 Any routine will likely consist of the same phases: first kiss, rhythm, tension, escalation, preorgasm and orgasm.
\1 You have a tongue, fingertips, palms and gums to use.
\end{outline}

\section{Routines: Beginner to Advanced}
(It's already a summary in the book, so I can't compress it.)

\section*{Conclusion}
When she comes first, she comes forever.

\section*{Appendix 1: Manual Stimulation for Foreplay}
Lie flat on your backs next to each other. Drape your arm over her abdomen. The idea is now to rub her like she would masturbate.
\begin{enumerate}
	\item Gently explore the area with one finger. Dip it into her vagina like you would in a still pond.
	\item Rub her clitoral head in gentle circles.
	\item Tickle the frenulum.
	\item Push the skin from front commissure towards the head. Give the head a GENTLE squeeze.
	\item Hook two fingers in and start massaging behind the head, left to right.
	\item Flatten your hand and lay it over her vulva while she grinds into it.
	\item Repeat. 
\end{enumerate}
